Presentation Title

### 2017-08-30 paper/s1-intro.tex
Edit paper before defence

% problem description
Bitcoin is almost ten years old, and its market capitalisation is over \$60 billion USD and growing~\cite{bitcoinmarketcap}.
We can be reasonably sure that cryptocurrencies,
even if their application is still somewhat limited,
are here to stay in the foreseeable future.
Driven by the success of Bitcoin, we see a renaissance of consensus research~\cite{miller2016honey, kogias2016enhancing, kokoris2017omniledger},
where the primary focus is to improve the scalability of blockchain systems,
which is due to the inefficiencies of the consensus mechanism---proof-of-work (PoW).
For example, Bitcoin can only do 7 transactions per second (TPS) at most~\cite{vukolic2015quest}.
While adjusting the block size (which Bitcoin has recently done via SegWit~\cite{segwit}) and/or the block interval may increase TPS,
it also leads to centralisation as larger blocks take longer to propagate through the network,
putting miners that do not have a fast network at a disadvantage~\cite{croman2016scaling}.
Furthermore, due to the bandwidth and latency of today's network,
it is not possible to achieve more than 27 TPS from simply adjusting the block size or block interval~\cite{croman2016scaling}.

\textbf{Related work.\quad}
Many approaches exist for improving the scalability of early blockchain systems.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is needed.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
Each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of her Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Moreover, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, leading to centralisation.

@@

Finally, a technique that does achieve horizontal scalability is sharding, e.g., Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}.
It involves grouping nodes into multiple committees of constant size, also known as shards,
and nodes within a single shard run a Byzantine consensus algorithm to agree on a set of transactions that belong to that specific shard.
The number of shards grows linearly with respect to the total computational power of the network;
hence the transaction rate also grows linearly.
The limitation of sharding is that it is only optimal if transactions stay in the same shard.
In fact, Elastico cannot atomically process inter-shard transactions.
OmniLedger has an inter-shard transaction protocol but choosing a good shard size is difficult.
A large shard size would degrade the transaction throughput because the Byzantine consensus algorithm must be run by a large number of nodes.
A small shard size would result in a large number of inter-shard transactions which hinders scalability.
% The authors of OmniLedger noted that inter-shard transactions have significantly higher latency compared to the consensus protocol~\cite{kokoris2017omniledger}.

>>>>

% problem description
The first blockchain system---Bitcoin---is almost ten years old. 
Its market capitalisation is over \$60 billion USD and growing~\cite{bitcoinmarketcap}.
We can be reasonably sure that such systems,
even if their application is still somewhat limited,
are here to stay in the foreseeable future.
Driven by the success of Bitcoin, we see a renaissance of consensus research~\cite{luu2016elastico, kogias2016enhancing, kokoris2017omniledger},
where the primary focus is to improve the scalability of blockchain systems,
which is due to the inefficiencies of the consensus mechanism---proof-of-work (PoW).
For example, Bitcoin can only do 7 transactions per second (TPS) at most~\cite{vukolic2015quest}.
While adjusting the block size (which Bitcoin has recently done via SegWit~\cite{segwit}) and/or the block interval may increase TPS,
it also leads to centralisation as larger blocks take longer to propagate through the network,
putting miners that do not have a fast network at a disadvantage~\cite{croman2016scaling}.
Furthermore, due to the bandwidth and latency of today's network,
it is not possible to achieve more than 27 TPS from simply adjusting the block size or block interval~\cite{croman2016scaling}.

\textbf{Related work.\quad}
Many approaches exist for improving the scalability of early blockchain systems.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is needed.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
Each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of her Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Moreover, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, leading to centralisation.
% TODO other side-chain schemes? polkadot? perum? dfinity?

@@

Finally, a technique that does achieve horizontal scalability is sharding, e.g., Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}.
It involves grouping nodes into multiple committees of constant size, also known as shards,
and nodes within a single shard run a Byzantine consensus algorithm to agree on a set of transactions that belong to that specific shard.
The number of shards grows linearly with respect to the total computational power of the network;
hence the transaction rate also grows linearly.
The limitation of sharding is that it is only optimal if transactions stay in the same shard.
In fact, Elastico cannot atomically process inter-shard transactions.
OmniLedger has an inter-shard transaction protocol but choosing a shard size that matches the transaction characteristics of the network is difficult.
An inadequate shard size would result in a large number of inter-shard transactions which would hinder scalability.
% The authors of OmniLedger noted that inter-shard transactions have significantly higher latency compared to the consensus protocol~\cite{kokoris2017omniledger}.

### 2017-08-30 paper/s2-problem.tex
Edit paper before defence

\section{Problem Description}
\label{sec:description}
We introduce the problem as a modified Byzantine consensus problem.
The modification is primarily derived from the need of horizontal scalability,
which is not a part of a typical Byzantine consensus problem.
In our model, we consider $N$ nodes, $t$ of which are Byzantine.
Nodes in our system make transactions with each other.
Transactions can be in one of three states---\emph{valid}, \emph{invalid} and \emph{unknown}.
We seek a protocol that satisfies the following properties.
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or decide \emph{unknown}.
    \item \emph{Scalability}:
        If every node makes transactions at the same rate,
        then as $N$ increases,
        the global transaction rate should increase linearly w.r.t. $N$.
\end{itemize}

Note that the agreement property is similar, but a relaxed version of what is often seen in a Byzantine consensus problem.
Namely, the property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Our problem does not have a termination property, also known as liveness.
Instead, nodes are incentivised to complete the protocol execution;
we describe this phenomenon in~\Cref{sec:correctness-of-validity}.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This formulation is so that the protocol can act as a building block to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as the accounting of internet traffic in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do have fork detection in~\Cref{sec:fork}.

>>>>

\section{Problem Description}
\label{sec:description}
We introduce the problem as a modified Byzantine consensus problem.
The modification is primarily derived from the need of horizontal scalability,
which is not a part of a typical Byzantine consensus problem.
In our model, we consider $N$ nodes, $t$ of which are Byzantine.
Nodes in our system make transactions with each other.
Transactions can be in one of three states---\emph{valid}, \emph{invalid} and \emph{unknown}.
We seek a protocol that satisfies the following properties.
\begin{itemize}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or decide \emph{unknown}.
    \item \emph{Validity}:
        If a transaction is valid, then it must have been created by two honest nodes.
    \item \emph{Scalability}:
        If every node makes transactions at the same rate,
        then as $N$ increases,
        the global transaction rate should increase linearly w.r.t. $N$.
\end{itemize}

Note that the agreement property is similar, but a relaxed version of what is often seen in a Byzantine consensus problem.
Namely, the property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Our problem does not have a termination property, also known as liveness.
Instead, nodes are incentivised to complete the protocol execution otherwise they risk economical loss;
we describe this phenomenon in~\Cref{sec:correctness-of-validity}.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This formulation is so that the protocol can act as a building block to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as the accounting of internet traffic in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do have fork detection in~\Cref{sec:fork}.
% TODO our transactions are rather different from a typical cryptocurrency transaction,
% should we still call it transactions or something else?

### 2017-08-30 paper/s3-system.tex
Edit paper before defence

Early blockchain systems that use a global ledger are difficult to scale because every node must reach consensus on all the transactions that ever existed.
Instead, we introduce an alternative architecture where every node has their own genesis block and hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks, and every block only contains one transaction.
A transaction between two nodes should, therefore, result in two TX blocks on their respective hash chains.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Then, a collection of CP blocks from all nodes would represent the state of the whole system.
A visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the data structure used in \textsc{Checo}.
$t_{u, i}$ represents a TX block on $u$'s chain with a sequence number $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number $j$.
The blocks at the ends of the dotted lines are pairs of each other.
Blocks of sequence number 0 (e.g., $t_{c, 0}$) are genesis blocks.}
\label{fig:trustchain-good-cp}
\end{figure}

@@

\begin{definition}
\textbf{\emph{Transaction block}}

@@

TX blocks come in pairs.
In particular, for every block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exist one and only one \emph{pair} 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle,$$
if the nodes follow the transaction protocol (described in~\Cref{sec:tx-protocol}).
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

\begin{definition}
\textbf{\emph{Checkpoint block and genesis block}}

@@

The genesis block in the chain must be a CP block in the form of
$$c_{u, 0} = \langle \textsf{H}(\bot), 0,  \textsf{H}(\bot), 0, sig_u \rangle,$$
where $\textsf{H}(\bot)$ can be interpreted as applying the hash function on an empty string.
The genesis block is unique because every node has a unique public and private key pair.
\end{definition}

\begin{definition}
\label{sec:consensus-result}
\textbf{\emph{Consensus result}}

@@

Here we define a property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol (discussed in~\Cref{sec:vd-protocol}).

\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$, where
\begin{itemize}
\item $c_{u, a}$ is the closest CP block to $t_{u, i}$ with a lower sequence number and
\item $c_{u, b}$ is the closest CP block to $t_{u, i}$ with a higher sequence number,
\end{itemize}
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Some TX blocks may not have any enclosure, then their enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

\begin{definition}
\textbf{\emph{Fragment and agreed fragment}}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol $\Pi_c$ uses an unmodified asynchronous common subset (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\emph{\textsc{Checo} consensus protocol}}

@@

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h-1} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits until $N - t$ messages of type \texttt{cp\_msg} are received.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed.
That is blocks with invalid signatures and blocks signed by the same key.
With the sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

@@

\subsubsection{Validation Protocol}
Our validation protocol $\Pi_v$,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{\textsc{Checo} validation protocol}}

@@

\subsection{Using Timing Assumption in the Permissionless Setting}
\label{sec:permissionless}
At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
The use of $N$ makes our system unsuitable for the permissionless setting.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsection{Total Fork Detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment,
which is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

>>>>

Early blockchain systems that use a global ledger are difficult to scale because every node must reach consensus on all the transactions that ever existed.
Instead, we introduce an alternative architecture where every node has their own genesis block and hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chains.
Transactions are stored in TX blocks, and every block only contains one transaction.
A transaction between two nodes should, therefore, result in two TX blocks on their respective hash chains.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Then, a collection of CP blocks from all nodes would represent the state of the whole system.
A visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the data structure used in \textsc{Checo}.
$t_{u, i}$ represents a TX block on $u$'s chain with a sequence number $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number $j$.
The blocks at the ends of the dotted lines are pairs of each other.
Blocks of sequence number 0 (e.g., $t_{c, 0}$) are genesis blocks.}
\label{fig:trustchain-good-cp}
\end{figure}

@@

\begin{definition}
\textbf{Transaction block}

@@

TX blocks come in pairs.
In particular, for every block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exists one and only one \emph{pair} 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle,$$
if the nodes follow the transaction protocol (described in~\Cref{sec:tx-protocol}).
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

\begin{definition}
\textbf{Checkpoint block and genesis block}

@@

The genesis block in the chain must be a CP block in the form of
$$c_{u, 0} = \langle \textsf{H}(\epsilon), 0,  \textsf{H}(\epsilon), 0, sig_u \rangle,$$
where $\epsilon$ is the empty string.
The genesis block is unique because every node has a unique public and private key pair.
\end{definition}

\begin{definition}
\label{sec:consensus-result}
\textbf{Consensus result}

@@

Next we define a property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol (discussed in~\Cref{sec:vd-protocol}).

\begin{definition}
\textbf{Enclosure and agreed enclosure}

If there exists a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$, where
\begin{itemize}
\item $c_{u, a}$ is the closest CP block to $t_{u, i}$ with a lower sequence number and
\item $c_{u, b}$ is the closest CP block to $t_{u, i}$ with a higher sequence number,
\end{itemize}
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Some TX blocks may not have any enclosure, then their enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

\begin{definition}
\textbf{Fragment and agreed fragment}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol $\Pi_c$ uses an unmodified asynchronous common subset (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\textsc{Checo} consensus protocol}

@@

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h-1} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits until $N - t$ messages of type \texttt{cp\_msg} are received.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed.
Those are blocks with invalid signatures and blocks signed by the same key.
With the sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

@@

\subsubsection{Validation Protocol}
Our validation protocol $\Pi_v$,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties are as follows.
\begin{definition}
\label{def:validation}
\textbf{\textsc{Checo} validation protocol}

@@

\subsection{Open membership using timing assumption}
\label{sec:permissionless}
At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
The use of $N$ makes our system unsuitable for the open membership setting,
where nodes may join and leave at will (churn).
We over come this problem by introducing a timing assumption.
Concretely, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

@@

\subsection{Total Fork Detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment,
which is sufficient for some applications such as proving the existence of some information.
However, for applications such as cryptocurrency where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.
